---
title: "QuasiFlow NGS-Based HIV Drug Resistance Report"
params:
  dr_report_hydra: ""
  dr_report_hivdb: ""
  mutation_comments: ""
  mutational_threshold: 0.01
  minimum_read_depth: 100
  minimum_percentage_cons: 20
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    #vertical_layout: fill
    vertical_layout: scroll
    theme: spacelab #simplex #flatly
    css: "custom.css"
---

```{r setup, include=FALSE}
require(knitr)
library(flexdashboard)
require(kableExtra)
```

```{r, eval=TRUE}
generate_dr_report<-function(path){
  hivdr <- jsonlite::fromJSON(path, flatten = TRUE)
tmp<-data.frame()
for (i in 1:dim(hivdr)[1]) {
  seq_df <- hivdr[i,]
  seq<-seq_df$inputSequence.header
  drug_res<-seq_df$drugResistance[[1]]
  genes<-drug_res$gene.name
  for (gene in unique(genes)) {
    gene_df<-drug_res[drug_res$gene.name==gene,]
    
    # extracted the version and date
    version <- gene_df$version.text
    verDate <- gene_df$version.publishDate
    gene_drug_scores<-gene_df$drugScores[[1]]
    gene_drug_scores<-gene_drug_scores[c("drugClass.name","drug.name", "score", "text")]
    tmp<-rbind(tmp, gene_drug_scores)
    }
  names(tmp)<-c("drugClass.name", "Drug name", "HIVDB Score", "Drug susceptibility")
  mutations<-seq_df$alignedGeneSequences[[1]]$mutations
  subtype<-hivdr$subtypeText
  AApositions<-hivdr[[3]][[1]]
  AApositions<-AApositions[c("firstAA","lastAA","gene.name")]
  drugScores_comments<-hivdr$drugResistance[[1]]$drugScores
}
out<-list(seq=seq, genes=genes, drugscores=tmp, mutations=mutations, version=version, version_date=verDate, subtype=subtype,AApositions=AApositions,comments=drugScores_comments)
return(out)
}
```

```{r eval=TRUE, echo=FALSE}
get_comments<-function(drug_scores,index){
  mut_comments<-drug_scores[[index]]$partialScores[[1]]$mutations
  comments<-data.frame()
  if (length(mut_comments)>0){
    for (i in 1:length(mut_comments)) {
      mut<-mut_comments[[i]]$text
      type<-mut_comments[[i]]$primaryType
      tmp<-data.frame(mut_comments[[i]]$comments)
      comm<-tmp$text
      tmp<-data.frame(Mutation=mut, Type=type, Comment=comm)
      comments<-rbind(comments,tmp)
    }  
  }
  comments
}
```

```{r}
hivdr<-generate_dr_report(params$dr_report_hivdb)
seq<-hivdr$seq
seq<-sub("_.*","",hivdr$seq)
genes<-hivdr$genes
mutations<-hivdr$mutations
tmp<-hivdr$drugscores
AApositions<-hivdr$AApositions
comments<-hivdr$comments
write.csv(tmp, file=paste0(seq,"_drugscores.csv"), quote=FALSE)
# added the algorithm version and date
version <- paste("HIVDB", hivdr$version, sep = " ")
verDate <- paste0("(",hivdr$version_date, ")" )
version_date <- paste(version, verDate, sep=" ")

```

```{r}
#comments <- read.csv(params$mutation_comments,strip.white=T)
```


```{r}
PR_major = ""
PR_accessory = ""
PR_Other = ""
PR_comments_list = NULL
firstAA_PR=""
lastAA_PR=""

if("PR"%in%genes){
  PR_mutations<-mutations[[which(AApositions$gene.name=="PR")]]
  PR_mutations<-paste0(PR_mutations$consensus, PR_mutations$position, PR_mutations$AAs)
  PR_comments <- get_comments(comments, 1) #comments[comments$Mutation%in%PR_mutations,]
  PR_major<-PR_comments$Mutation[PR_comments$Type=="Major"]
  PR_accessory<-PR_comments$Mutation[PR_comments$Type=="Accessory"]
  PR_Other<-PR_mutations[!PR_mutations%in%c(PR_major,PR_accessory)]
  PR_comments_list<-PR_comments$Comment
  firstAA_PR=AApositions$firstAA[AApositions$gene.name=="PR"]
  lastAA_PR=AApositions$lastAA[AApositions$gene.name=="PR"]
  }

RT_NNRTI = ""
RT_NRTI = ""
RT_Other = ""
RT_comments_list = NULL
firstAA_RT=""
lastAA_RT=""

if("RT"%in%genes){
  RT_mutations<-mutations[[which(AApositions$gene.name=="RT")]]
  RT_mutations<-paste0(RT_mutations$consensus, RT_mutations$position, RT_mutations$AAs)
  RT_comments <- get_comments(comments, 2) #comments[comments$Mutation%in%RT_mutations,]
  RT_NNRTI<-RT_comments$Mutation[RT_comments$Type=="NNRTI"]
  RT_NRTI<-RT_comments$Mutation[RT_comments$Type=="NRTI"]
  RT_Other<-RT_mutations[!RT_mutations%in%c(RT_NNRTI,RT_NRTI)]
  RT_comments_list<-RT_comments$Comment
  firstAA_RT=AApositions$firstAA[AApositions$gene.name=="RT"]
  lastAA_RT=AApositions$lastAA[AApositions$gene.name=="RT"]
}

IN_major=""
IN_accessory=""
IN_Other=""
IN_comments_list=NULL
firstAA_IN=""
lastAA_IN=""

if("IN"%in%genes){
  IN_mutations<-mutations[[which(AApositions$gene.name=="IN")]]
  IN_mutations<-paste0(IN_mutations$consensus, IN_mutations$position, IN_mutations$AAs)
  IN_comments <- get_comments(comments, 3) #comments[comments$Mutation%in%IN_mutations,]
  IN_major<-IN_comments$Mutation[IN_comments$Type=="Major"]
  IN_accessory<-IN_comments$Mutation[IN_comments$Type=="Accessory"]
  IN_Other<-IN_mutations[!IN_mutations%in%c(IN_major,IN_accessory)]
  IN_comments_list<-IN_comments$Comment
  firstAA_IN=AApositions$firstAA[AApositions$gene.name=="IN"]
  lastAA_IN=AApositions$lastAA[AApositions$gene.name=="IN"]
}

mutationList_display<-function(x){
  if(length(x)==0){
    return("None")
  }else{
    return(x)
  }
}
```

<!-- Credits: Quasitools, Hydra, Sierralocal, HIVdb. -->

Row 1
-----------------------------------------------------------------------

### **Sequence summary**

**Query ID**: `r seq`

**Sequence includes**: `r genes`

**Sequence subtype**: `r hivdr$subtype`

### **Basic pipeline parameters**

**Minimum mutation frequency**: `r paste0(params$mutational_threshold)`

**Minimum percentage a base needs to be incorportated into the consensus sequence**: `r paste0(params$minimum_percentage_cons)`

**Minimum read depth**: `r params$minimum_read_depth`



Row 2
-----------------------------------------------------------------------
### **Drug Resistance Interpretation: PR**

**Algorithm version**: `r version_date`

**PI Major Mutations**: `r mutationList_display(PR_major)`

**PI Accessory Mutations**: `r mutationList_display(PR_accessory)`

**PR Other Mutations**: `r mutationList_display(PR_Other)`

**Comments**: 

```{r}
colnames(PR_comments_list)<-NULL
PR_comments_list %>% 
  kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F) %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%", height = "150px")
```

### **Mutation HIVDR Scores: PR**

```{r}
PR_df<-tmp[tmp$drugClass.name=="PI",]
PR_df[2:4] %>% 
kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F, align="c") %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%", height = "300px")
```

Row 3
-----------------------------------------------------------------------
### **Drug Resistance Interpretation: RT**

**Algorithm version**: `r version_date`

**NNRTI Resistance Mutations**: `r mutationList_display(RT_NNRTI)`

**NRTI Resistance Mutations**: `r mutationList_display(RT_NRTI)`

**Other RT Mutations**: `r mutationList_display(RT_Other)`

**Comments**:

```{r}
colnames(RT_comments_list)<-NULL
RT_comments_list %>% 
  kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F) %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%", height = "110px")
```


#### **Drug resistance mutation scoring: NRTI**

```{r}
RT_df<-tmp[tmp$drugClass.name=="NRTI",]
RT_df[2:4] %>% 
 kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F, align="c") %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%")
```

### **Mutation HIVDR Scores: NNRTI**

```{r}
RT_df<-tmp[tmp$drugClass.name=="NNRTI",]
RT_df[2:4] %>% 
kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F, align="c") %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%")
```


Row 4
-----------------------------------------------------------------------

### **Drug Resistance Interpretation: IN**

**Algorithm version**: `r version_date`

**INI Major Mutations**: `r mutationList_display(IN_major)`

**INI Accessory Mutations**: `r mutationList_display(IN_accessory)`

**IN Other Mutations**: `r mutationList_display(IN_Other)`

**Comments**: 

```{r}
colnames(IN_comments_list)<-NULL
IN_comments_list %>% 
  kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F) %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%")
```


#### **Drug resistance mutation scoring: IN**
```{r}
IN_df<-tmp[tmp$drugClass.name=="INSTI",]
IN_df[2:4] %>% 
  kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F, align="c") %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%")
```
