---
title: "QuasiFlow NGS-Based HIV Drug Resistance Report"
params:
  dr_report_hydra: ""
  dr_report_hivdb: ""
  mutation_comments: ""
  mutational_threshold: 0.01
  minimum_read_depth: 100
  minimum_percentage_cons: 20
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    #vertical_layout: fill
    vertical_layout: scroll
    theme: spacelab #simplex #flatly
    css: "custom.css"
---

```{r setup, include=FALSE}
require(knitr)
library(flexdashboard)
require(plyr)
require(dplyr)
require(kableExtra)
```

```{r, eval=TRUE}
generate_dr_report<-function(path){
  hivdr <- jsonlite::fromJSON(path, flatten = TRUE)
tmp<-data.frame()
for (i in 1:dim(hivdr)[1]) {
  seq_df <- hivdr[i,]
  seq<-seq_df$inputSequence.header
  drug_res<-seq_df$drugResistance[[1]]
  genes<-drug_res$gene.name
  for (gene in unique(genes)) {
    gene_df<-drug_res[drug_res$gene.name==gene,]
    
    # extracted the version and date
    version <- gene_df$version.text
    verDate <- gene_df$version.publishDate
    gene_drug_scores<-gene_df$drugScores[[1]]
    gene_drug_scores<-gene_drug_scores[c("drugClass.name","drug.name", "score", "text")]
    tmp<-rbind(tmp, gene_drug_scores)
    }
  names(tmp)<-c("drugClass.name", "Drug name", "HIVDB Score", "Drug susceptibility")
  mutations<-seq_df$alignedGeneSequences[[1]]$mutations
  subtype<-hivdr$subtypeText
}
out<-list(seq=seq, genes=genes, drugscores=tmp, mutations=mutations, version=version, version_date=verDate, subtype=subtype)
return(out)
}
```

```{r}
hivdr<-generate_dr_report(params$dr_report_hivdb)
seq<-hivdr$seq
genes<-hivdr$genes
mutations<-hivdr$mutations
tmp<-hivdr$drugscores

# added the algorithm version and date
version <- paste("HIVDB", hivdr$version, sep = " ")
verDate <- paste0("(",hivdr$version_date, ")" )
version_date <- paste(version, verDate, sep=" ")
```

```{r}
comments <- read.csv(params$mutation_comments,strip.white=T)
```


```{r}
PR_mutations<-mutations[[1]]
PR_mutations<-paste0(PR_mutations$consensus, PR_mutations$position, PR_mutations$AAs)
PR_comments <- comments[comments$Mutation%in%PR_mutations,]
PR_major<-PR_comments$Mutation[PR_comments$Type=="Major"]
PR_accessory<-PR_comments$Mutation[PR_comments$Type=="Accessory"]
PR_Other<-PR_mutations[!PR_mutations%in%c(PR_major,PR_accessory)]
PR_comments_list<-PR_comments["Comment"]

RT_mutations<-mutations[[2]]
RT_mutations<-paste0(RT_mutations$consensus, RT_mutations$position, RT_mutations$AAs)
RT_comments <- comments[comments$Mutation%in%RT_mutations,]
RT_NNRTI<-RT_comments$Mutation[RT_comments$Type=="NNRTI"]
RT_NRTI<-RT_comments$Mutation[RT_comments$Type=="NRTI"]
RT_Other<-RT_mutations[!RT_mutations%in%c(RT_NNRTI,RT_NRTI)]
RT_comments_list<-RT_comments["Comment"]

IN_mutations<-mutations[[3]]
IN_mutations<-paste0(IN_mutations$consensus, IN_mutations$position, IN_mutations$AAs)
IN_comments <- comments[comments$Mutation%in%IN_mutations,]
IN_major<-IN_comments$Mutation[IN_comments$Type=="Major"]
IN_accessory<-IN_comments$Mutation[IN_comments$Type=="Accessory"]
IN_Other<-IN_mutations[!IN_mutations%in%c(IN_major,IN_accessory)]
IN_comments_list<-IN_comments["Comment"]

#Function to display mutation list or None 
mutationList_display<-function(x){
  if(length(x)==0){
    return("None")
  }else{
    return(x)
  }
}

```

<!-- Credits: Quasitools, Hydra, Sierralocal, HIVdb. -->

Row 1
-----------------------------------------------------------------------

### **Sequence summary**

**Query ID**: `r seq`

**Sequence includes**: `r genes`

**Sequence subtype**: `r hivdr$subtype`

### **Basic pipeline parameters**

**Minimum mutation frequency**: `r paste0(params$mutational_threshold)`

**Minimum percentage a base needs to be incorportated into the consensus sequence**: `r paste0(params$minimum_percentage_cons)`

**Minimum read depth**: `r params$minimum_read_depth`



Row 2
-----------------------------------------------------------------------
### **Drug Resistance Interpretation: PR**

**Algorithm version**: `r version_date`

**PI Major Resistance Mutations**: `r mutationList_display(PR_major)`

**PI Accessory Resistance Mutations**: `r mutationList_display(PR_accessory)`

**Other PR Mutations**: `r mutationList_display(PR_Other)`

**Comments**: 

```{r}
colnames(PR_comments_list)<-NULL
PR_comments_list %>% 
  kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F) %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%", height = "150px")
```

### **Mutation HIVDR Scores: PR**

```{r}
PR_df<-tmp[tmp$drugClass.name=="PI",]
PR_df[2:4] %>% 
kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F, align="c") %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%", height = "300px")
```

Row 3
-----------------------------------------------------------------------
### **Drug Resistance Interpretation: RT**

**Algorithm version**: `r version_date`

**NNRTI Resistance Mutations**: `r mutationList_display(RT_NNRTI)`

**NRTI Resistance Mutations**: `r mutationList_display(RT_NRTI)`

**Other RT Mutations**: `r mutationList_display(RT_Other)`

**Comments**:

```{r}
colnames(RT_comments_list)<-NULL
RT_comments_list %>% 
  kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F) %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%", height = "110px")
```


### **Mutation HIVDR Scores: NRTI**

```{r}
RT_df<-tmp[tmp$drugClass.name=="NRTI",]
RT_df[2:4] %>% 
 kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F, align="c") %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%")
```

### **Mutation HIVDR Scores: NNRTI**

```{r}
RT_df<-tmp[tmp$drugClass.name=="NNRTI",]
RT_df[2:4] %>% 
kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F, align="c") %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%")
```


Row 4
-----------------------------------------------------------------------

### **Drug Resistance Interpretation: INI**

**Algorithm version**: `r version_date`

**INI Major Resistance Mutations**: `r mutationList_display(IN_major)`

**INI Accessory Resistance Mutations**: `r mutationList_display(IN_accessory)`

**Other IN Mutations**: `r mutationList_display(IN_Other)`

**Comments**: 

```{r}
colnames(IN_comments_list)<-NULL
IN_comments_list %>% 
  kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F) %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%")
```


### **Mutation HIVDR Scores: INI**
```{r}
IN_df<-tmp[tmp$drugClass.name=="INSTI",]
IN_df[2:4] %>% 
  kableExtra::kable(booktabs = TRUE, longtable = TRUE, row.names=F, align="c") %>% kable_styling(latex_options = c("hold_position", 
    "repeat_header", position = "")) %>% scroll_box(width = "100%")
```
