---
title: "**NGS-Based HIV Drug Resistance Report**"
output: 
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: true
    
nocite: '@*'
bibliography: refs.bib

params:
  dr_report_hivdb: ""
  mutation_comments: ""
  mutational_threshold: 0
  minimum_read_depth: 0
  minimum_percentage_cons: 0
---

```{r setup, include=FALSE}
require(knitr)
require(plyr)
require(dplyr)
require(jsonlite)
require(tinytex)
#tinytex::install_tinytex()
```

```{r, eval=TRUE, echo=FALSE}
generate_dr_report<-function(path){
  hivdr <- jsonlite::fromJSON(path, flatten = TRUE)
  Drugscores<-data.frame()
for (i in 1:dim(hivdr)[1]) {
  seq_df <- hivdr[i,]
  seq<-seq_df$inputSequence.header
  drug_res<-seq_df$drugResistance[[1]]
  genes<-drug_res$gene.name
  for (gene in unique(genes)) {
    gene_df<-drug_res[drug_res$gene.name==gene,]
    # extracted the version and date
    version <- gene_df$version.text
    verDate <- gene_df$version.publishDate
    gene_drug_scores<-gene_df$drugScores[[1]]
    gene_drug_scores<-gene_drug_scores[c("drugClass.name","drug.name", "score", "text")]
    Drugscores<-rbind(Drugscores, gene_drug_scores)
    }
  names(Drugscores)<-c("drugClass.name", "Drug name", "HIVDB Score", "Drug susceptibility")
  mutations<-seq_df$alignedGeneSequences[[1]]$mutations
  subtype<-hivdr$subtypeText
  AApositions<-hivdr[[3]][[1]]
  AApositions<-AApositions[c("firstAA","lastAA","gene.name")]
  
  mut_comments<-hivdr$drugResistance[[1]]$drugScores[[1]]$partialScores[[1]]$mutations
  comments<-data.frame()
  if (length(mut_comments)>0){
    for (i in 1:length(mut_comments)) {
      mut<-mut_comments[[i]]$text
      type<-mut_comments[[i]]$primaryType
      tmp<-data.frame(mut_comments[[i]]$comments)
      comm<-tmp$text
      tmp<-data.frame(Mutation=mut, Type=type, Comment=comm)
      comments<-rbind(comments,tmp)
    }  
  }
}
out<-list(seq=seq, genes=genes, drugscores=Drugscores, mutations=mutations, version=version, version_date=verDate, subtype=subtype, AApositions=AApositions,comments=comments)
return(out)
}
```

```{r, eval=TRUE, echo=FALSE}
hivdr<-generate_dr_report(params$dr_report_hivdb)
seq<-sub("_.*","",hivdr$seq)
genes<-hivdr$genes
mutations<-hivdr$mutations
tmp<-hivdr$drugscores
AApositions<-hivdr$AApositions
comments<-hivdr$comments

# added the algorithm version and date
version <- paste("HIVDB", hivdr$version, sep = " ")
verDate <- paste0("(",hivdr$version_date, ")" )
version_date <- paste(version, verDate, sep=" ")
```

```{r, echo=FALSE}
#comments <- read.csv(params$mutation_comments,strip.white=T)
```


```{r, echo=FALSE}
PR_major = ""
PR_accessory = ""
PR_Other = ""
PR_comments_list = NULL
firstAA_PR=""
lastAA_PR=""

if("PR"%in%genes){
  PR_mutations<-mutations[[which(AApositions$gene.name=="PR")]]
  PR_mutations<-paste0(PR_mutations$consensus, PR_mutations$position, PR_mutations$AAs)
  PR_comments <- comments[comments$Mutation%in%PR_mutations,]
  PR_major<-PR_comments$Mutation[PR_comments$Type=="Major"]
  PR_accessory<-PR_comments$Mutation[PR_comments$Type=="Accessory"]
  PR_Other<-PR_mutations[!PR_mutations%in%c(PR_major,PR_accessory)]
  PR_comments_list<-PR_comments$Comment
  firstAA_PR=AApositions$firstAA[AApositions$gene.name=="PR"]
  lastAA_PR=AApositions$lastAA[AApositions$gene.name=="PR"]
  }

RT_NNRTI = ""
RT_NRTI = ""
RT_Other = ""
RT_comments_list = NULL
firstAA_RT=""
lastAA_RT=""

if("RT"%in%genes){
  RT_mutations<-mutations[[which(AApositions$gene.name=="RT")]]
  RT_mutations<-paste0(RT_mutations$consensus, RT_mutations$position, RT_mutations$AAs)
  RT_comments <- comments[comments$Mutation%in%RT_mutations,]
  RT_NNRTI<-RT_comments$Mutation[RT_comments$Type=="NNRTI"]
  RT_NRTI<-RT_comments$Mutation[RT_comments$Type=="NRTI"]
  RT_Other<-RT_mutations[!RT_mutations%in%c(RT_NNRTI,RT_NRTI)]
  RT_comments_list<-RT_comments$Comment
  firstAA_RT=AApositions$firstAA[AApositions$gene.name=="RT"]
  lastAA_RT=AApositions$lastAA[AApositions$gene.name=="RT"]
}

IN_major=""
IN_accessory=""
IN_Other=""
IN_comments_list=NULL
firstAA_IN=""
lastAA_IN=""

if("IN"%in%genes){
  IN_mutations<-mutations[[which(AApositions$gene.name=="IN")]]
  IN_mutations<-paste0(IN_mutations$consensus, IN_mutations$position, IN_mutations$AAs)
  IN_comments <- comments[comments$Mutation%in%IN_mutations,]
  IN_major<-IN_comments$Mutation[IN_comments$Type=="Major"]
  IN_accessory<-IN_comments$Mutation[IN_comments$Type=="Accessory"]
  IN_Other<-IN_mutations[!IN_mutations%in%c(IN_major,IN_accessory)]
  IN_comments_list<-IN_comments$Comment
  firstAA_IN=AApositions$firstAA[AApositions$gene.name=="IN"]
  lastAA_IN=AApositions$lastAA[AApositions$gene.name=="IN"]
}

mutationList_display<-function(x){
  if(length(x)==0){
    return("None")
  }else{
    return(unique(x))
  }
}
```

## **Sequence summary**

**Query ID**: `r seq`

**Sequence includes**: `r genes`

**Sequence subtype**: `r hivdr$subtype`

## **Basic pipeline parameters**

**Minimum mutation frequency**: `r paste0(params$mutational_threshold)`

**Minimum percentage a base needs to be incorportated into the consensus sequence**: `r paste0(params$minimum_percentage_cons)`

**Minimum read depth**: `r params$minimum_read_depth`


## **Drug Resistance Interpretation: PR**

**First AA**: `r firstAA_PR`     

**Last AA**:  `r lastAA_PR` 

**Algorithm version**: `r version_date`

**PI Major Resistance Mutations**: `r mutationList_display(PR_major)`

**PI Accessory Resistance Mutations**: `r mutationList_display(PR_accessory)`

**Other PR Mutations**: `r mutationList_display(PR_Other)`

**Comments**: `r if(length(PR_comments_list)<1){"None"}`

```{r, echo=FALSE}
if(length(PR_comments_list)>0){
  PR_comments_list<-data.frame(unique(PR_comments_list))
  names(PR_comments_list)<-""
  knitr::kable(unique(PR_comments_list), align = "l", row.names=FALSE)
}
```

#### **Mutation HIVDR Scores: PR**

```{r,echo=FALSE}
PR_df<-tmp[tmp$drugClass.name=="PI",]
knitr::kable(PR_df[2:4], row.names=FALSE)  
```
\newpage

## **Drug Resistance Interpretation: RT**

**First AA**: `r firstAA_RT`     

**Last AA**:  `r lastAA_RT` 

**Algorithm version**: `r version_date`

**NNRTI Resistance Mutations**: `r mutationList_display(RT_NNRTI)`

**NRTI Resistance Mutations**: `r mutationList_display(RT_NRTI)`

**Other RT Mutations**: `r mutationList_display(RT_Other)`

**Comments**: `r if(length(RT_comments_list)<1){"None"}`

```{r,echo=FALSE}
if(length(RT_comments_list)>0){
  RT_comments_list<-data.frame(unique(RT_comments_list))
  colnames(RT_comments_list)<-""
  knitr::kable(RT_comments_list, align = "l", row.names=FALSE)
}
```

#### **Mutation HIVDR Scores: NRTI**

```{r,echo=FALSE}
RT_df<-tmp[tmp$drugClass.name=="NRTI",]
if(dim(RT_df)[1]>1){
 knitr::kable(RT_df[2:4], row.names=FALSE)  
}
```

#### **Mutation HIVDR Scores: NNRTI**

```{r,echo=FALSE}
RT_df<-tmp[tmp$drugClass.name=="NNRTI",]
knitr::kable(RT_df[2:4], row.names=FALSE)  
```

\newpage

## **Drug Resistance Interpretation: IN**

**First AA**: `r firstAA_IN`     

**Last AA**:  `r lastAA_IN` 

**Algorithm version**: `r version_date`

**INI Major Resistance Mutations**: `r mutationList_display(IN_major)`

**INI Accessory Resistance Mutations**: `r mutationList_display(IN_accessory)`

**Other IN Mutations**: `r mutationList_display(IN_Other)`

**Comments**: `r if(length(IN_comments_list)<1){"None"}`

```{r,echo=FALSE}
if(length(IN_comments_list)>0){
  IN_comments_list<-data.frame(unique(IN_comments_list))
  colnames(IN_comments_list)<-""
  knitr::kable(IN_comments_list, align = "l", row.names=FALSE) 
}
```

#### **Mutation HIVDR Scores: INI**
```{r,echo=FALSE}
IN_df<-tmp[tmp$drugClass.name=="INSTI",]
if(dim(RT_df)[1]>1){
 knitr::kable(IN_df[2:4], row.names=FALSE)  
}
```

## **References**
